---
title: "Statistical analyses of behavioral data from the Eriksen Flanker Task"
author: "Louise Bruland Bjerrum"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages

```{r}
library(tidyverse)
library(lmerTest)
library(merDeriv)
library(glmmTMB)
library(DHARMa)
library(easystats)
library(emmeans)
library(ggpubr)
library(ggsignif)
library(extrafont)
```


# Import aggregated dataset

```{r}
Flanker_data <- read_csv("EFT_dataset.csv") #change relative path as needed
```


# Clean data

```{r}
Flanker_data <- Flanker_data %>%   
  mutate(Light = as_factor(Light)) %>% 
  filter(Subject != 1057) #exclude subject with no actigraphy data and unreliable sleep diary entries 
```

*Exclude observations for subjects tested in abnormally high and low temperatures (measurement errors)*

```{r}
excluded_subjects <- c(1016, 1023, 1024, 1026, 1030) #define as list of subjects who's observations in white and dim light are measurement errors of abnormally high and low temperature during cognitive testing in the lab
```

```{r}
Flanker_data <- Flanker_data %>% 
  mutate(across(c(RT_compatible,
                  RT_incompatible,
                  IIV_RT_compatible,
                  IIV_RT_incompatible,
                  Conflict_effect_score,
                  Accuracy_compatible,
                  Accuracy_incompatible),
                ~ if_else(Subject %in% excluded_subjects & (Light == "BWL" | Light == "DL"), NA_real_, .))) #replace error observations in dim and white light with "NA" in outcome variables for the excluded subjects on the list 
```


# Re-level categorical predictor prior to analyses

```{r}
Flanker_data$Light <- relevel(Flanker_data$Light, ref = "DL") #dim light serves as reference level 
```


# Statistical analyses of main outcomes from the Eriksen Flanker Task 

## Intra-individual reaction time variability in the incompatible (conflict) flanker task condition

*Fit linear mixed-effects model, check model assumptions and extract performance metrics* 

```{r}
set.seed(123)

IIV_RT_incompatible_mod <- lmer(IIV_RT_incompatible ~ RT_incompatible + Light + IIV_TST + (1 | Subject), 
                               data = Flanker_data
                               )
```

```{r}
performance::check_model(IIV_RT_incompatible_mod)

plot(DHARMa::simulateResiduals(IIV_RT_incompatible_mod))
```

```{r}
performance::model_performance(IIV_RT_incompatible_mod)
```

*Extract results and modelbased parameters* 

```{r}
summary(IIV_RT_incompatible_mod)
```

```{r}
parameters::model_parameters(IIV_RT_incompatible_mod)
```

*Calculate approximated partial Cohen's f^2 as effect size for all fixed effects irrespective of significance, based on test statistics (output from summary() above)*

Mean RT: 

```{r}
effectsize::t_to_f2(t = 12.801, df = 107.27686, ci = 0.95, partial = TRUE)
```

SWL:

```{r}
effectsize::t_to_f2(t = -2.200, df = 106.29473, ci = 0.95, partial = TRUE)
```

LWL:

```{r}
effectsize::t_to_f2(t = -1.363, df = 106.53794, ci = 0.95, partial = TRUE)
```

BWL:

```{r}
effectsize::t_to_f2(t = -1.242, df = 103.52668, ci = 0.95, partial = TRUE)
```

Intra-individual sleep variability:

```{r}
effectsize::t_to_f2(t = 1.158, df = 56.09842, ci = 0.95, partial = TRUE)
```

*Obtain estimated marginal means for the significant main effect of light* 

```{r}
emmeans_IIVRTincompatible_light <- emmeans(IIV_RT_incompatible_mod, specs = ~ Light)
emmeans_IIVRTincompatible_light_df <- summary(as.data.frame(emmeans_IIVRTincompatible_light))
emmeans_IIVRTincompatible_light_df
```

*Plot of estimated marginal means for the main effect of light* 

```{r}
IIVRT_incompatible_light_plot <- ggplot(emmeans_IIVRTincompatible_light_df, aes(x = Light, y = emmean, fill = Light)) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 0.2, size = 0.7) +
  geom_point(aes(fill = Light), size = 7, color = "black", shape = 22, stroke = 0.7, show.legend = FALSE) +
  scale_fill_manual(values = c("dimgrey", "blue", "red", "lightblue1")) +
  scale_y_continuous(limits = c(105,160), breaks = seq(105, 155, by = 10)) +
  labs(
    x = "Light condition",
    y = "RTV (ms) in the incompatible\nflanker condition",
    fill = "Light"
    ) +
  theme_minimal() +
  theme(aspect.ratio = 1,
        plot.background = element_rect(fill = "white", color = NA),
        panel.background = element_rect(fill = "white", color = NA),
        plot.margin = margin(t = 2,
                             r = 2,
                             b = 2,
                             l = 2,
                             unit = "mm"),
        panel.grid = element_blank(), 
        panel.border = element_blank(),
        text = element_text(color = "black", family = "Arial", size = 10),
        axis.ticks = element_line(color = "black"),
        axis.line = element_line(color = "black"),
        axis.text.x = element_text(color = "black", family = "Arial", size = 10),
        axis.title.x = element_text(color = "black", family = "Arial", size = 10, margin = margin(t = 3, unit = "mm")),
        axis.title.y = element_text(color = "black", family = "Arial", size = 10, margin = margin(r = 3, unit = "mm")),
        axis.text.y = element_text(color = "black", family = "Arial", size = 10)
        ) +
   geom_signif(
    comparisons = list(c("DL", "SWL")),
    annotations = "*",
    y_position = 152,
    tip_length = 0.03
  )

IIVRT_incompatible_light_plot
```

```{r}
ggsave("IIVRT_incompatible_light_plot.tiff",
       plot = IIVRT_incompatible_light_plot,
       device = "tiff",
       width = 12,
       height = 12,
       units = "cm",
       dpi = 300)
```


## Differential incompatible-compatible reaction time score ("conflict effect score")

*Fit linear mixed-effects model, check model assumptions and extract performance metrics* 

```{r}
set.seed(123)

conflict_effect_mod <- lmer(Conflict_effect_score ~ Light + IIV_TST + (1 | Subject),
                            data = Flanker_data
                            )
```

```{r}
performance::check_model(conflict_effect_mod)

plot(DHARMa::simulateResiduals(conflict_effect_mod))
```

```{r}
performance::model_performance(conflict_effect_mod)
```

*Extract results and modelbased parameters* 

```{r}
summary(conflict_effect_mod)
```

```{r}
parameters::model_parameters(conflict_effect_mod)
```

*Calculate approximated partial Cohen's f^2 as effect size for all fixed effects irrespective of significance, based on test statistics (output from summary() above)*

SWL:

```{r}
effectsize::t_to_f2(t = 0.016, df = 103.50972, ci = 0.95, partial = TRUE)
```

LWL:

```{r}
effectsize::t_to_f2(t = 0.839, df = 103.83153, ci = 0.95, partial = TRUE)
```

BWL:

```{r}
effectsize::t_to_f2(t = 0.509, df = 102.28083, ci = 0.95, partial = TRUE)
```

Intra-individual sleep variability:

```{r}
effectsize::t_to_f2(t = -0.462, df = 105.88518, ci = 0.95, partial = TRUE)
```

*Obtain estimated marginal means for the main effect of light* 

```{r}
emmeans_conflict_effect_light <- emmeans(conflict_effect_mod, specs = ~ Light)
emmeans_conflict_effect_light_df <- summary(as.data.frame(emmeans_conflict_effect_light))
emmeans_conflict_effect_light_df
```

*Plot of estimated marginal means for the main effect of light* 

```{r}
conflict_effect_light_plot <- ggplot(emmeans_conflict_effect_light_df, aes(x = Light, y = emmean, fill = Light)) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 0.2, size = 0.7) +
  geom_point(aes(fill = Light), size = 7, color = "black", shape = 22, stroke = 0.7, show.legend = FALSE) +
  scale_y_continuous(limits = c(70,125), breaks = seq(70, 120, by = 10)) +
  scale_fill_manual(values = c("dimgrey", "blue", "red", "lightblue1")) +
  scale_x_discrete(labels = c("DL", "SWL", "LWL", "BWL")) +
  labs(
    x = "Light condition",
    y = "Differential incompatible-compatible\nRT score",
    fill = "Light"
    ) +
  theme_minimal() +
  theme(aspect.ratio = 1,
        plot.background = element_rect(fill = "white", color = NA),
        panel.background = element_rect(fill = "white", color = NA),
        plot.margin = margin(t = 2,
                             r = 2,
                             b = 2,
                             l = 2,
                             unit = "mm"),
        panel.grid = element_blank(), 
        panel.border = element_blank(),
        text = element_text(color = "black", family = "Arial", size = 10),
        axis.ticks = element_line(color = "black"),
        axis.line = element_line(color = "black"),
        axis.text.x = element_text(color = "black", family = "Arial", size = 10),
        axis.title.x = element_text(color = "black", family = "Arial", size = 10, margin = margin(t = 3, unit = "mm")),
        axis.title.y = element_text(color = "black", family = "Arial", size = 10, margin = margin(r = 3, unit = "mm")),
        axis.text.y = element_text(color = "black", family = "Arial", size = 10)
        )

conflict_effect_light_plot
```

```{r}
ggsave("conflict_effect_light_plot.tiff",
       plot = conflict_effect_light_plot,
       device = "tiff",
       width = 12,
       height = 12,
       units = "cm",
       dpi = 300)
```


## Intra-individual reaction time variability in the compatible (no conflict) flanker task condition 

*Fit linear mixed-effects model, check model assumptions and extract performance metrics* 

```{r}
set.seed(123)

IIV_RT_compatible_mod <- lmer(IIV_RT_compatible ~ RT_compatible + Light + IIV_TST + (1 | Subject),
                             data = Flanker_data
                             )
```

```{r}
performance::check_model(IIV_RT_compatible_mod)

plot(DHARMa::simulateResiduals(IIV_RT_compatible_mod))
```

```{r}
performance::model_performance(IIV_RT_compatible_mod)
```

*Extract results and modelbased parameters* 

```{r}
summary(IIV_RT_compatible_mod)
```

```{r}
parameters::model_parameters(IIV_RT_compatible_mod)
```

*Calculate approximated partial Cohen's f^2 as effect size for all fixed effects irrespective of significance, based on test statistics (output from summary() above)*

Mean RT: 

```{r}
effectsize::t_to_f2(t = 12.175, df = 120.95243, ci = 0.95, partial = TRUE)
```

SWL:

```{r}
effectsize::t_to_f2(t = -0.239, df = 104.17235, ci = 0.95, partial = TRUE)
```

LWL:

```{r}
effectsize::t_to_f2(t = 0.455, df = 104.59115, ci = 0.95, partial = TRUE)
```

BWL:

```{r}
effectsize::t_to_f2(t = -0.041, df = 100.86326, ci = 0.95, partial = TRUE)
```

Intra-individual sleep variability:

```{r}
effectsize::t_to_f2(t = 0.121, df = 52.51107, ci = 0.95, partial = TRUE)
```

*Obtain estimated marginal means for the main effect of light* 

```{r}
emmeans_IIVRTcompatible_light <- emmeans(IIV_RT_compatible_mod, specs = ~ Light)
emmeans_IIVRTcompatible_light_df <- summary(as.data.frame(emmeans_IIVRTcompatible_light))
emmeans_IIVRTcompatible_light_df
```

*Plot of estimated marginal means for the main effect of light* 

```{r}
IIVRT_compatible_light_plot <- ggplot(emmeans_IIVRTcompatible_light_df, aes(x = Light, y = emmean, fill = Light)) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 0.2, size = 0.7) +
  geom_point(aes(fill = Light), size = 7, color = "black", shape = 22, stroke = 0.7, show.legend = FALSE) +
  scale_y_continuous(limits = c(105,160), breaks = seq(105, 155, by = 10)) +
  scale_fill_manual(values = c("dimgrey", "blue", "red", "lightblue1")) +
  scale_x_discrete(labels = c("DL", "SWL", "LWL", "BWL")) +
  labs(
    x = "Light condition",
    y = "RTV (ms) in the compatible\nflanker condition",
    fill = "Light"
    ) +
  theme_minimal() +
  theme(aspect.ratio = 1,
        plot.background = element_rect(fill = "white", color = NA),
        panel.background = element_rect(fill = "white", color = NA),
        plot.margin = margin(t = 2,
                             r = 2,
                             b = 2,
                             l = 2,
                             unit = "mm"),
        panel.grid = element_blank(), 
        panel.border = element_blank(),
        text = element_text(color = "black", family = "Arial", size = 10),
        axis.ticks = element_line(color = "black"),
        axis.line = element_line(color = "black"),
        axis.text.x = element_text(color = "black", family = "Arial", size = 10),
        axis.title.x = element_text(color = "black", family = "Arial", size = 10, margin = margin(t = 3, unit = "mm")),
        axis.title.y = element_text(color = "black", family = "Arial", size = 10, margin = margin(r = 3, unit = "mm")),
        axis.text.y = element_text(color = "black", family = "Arial", size = 10)
        ) 

IIVRT_compatible_light_plot
```

```{r}
ggsave("IIVRT_compatible_light_plot.tiff",
       plot = IIVRT_compatible_light_plot,
       device = "tiff",
       width = 12,
       height = 12,
       units = "cm",
       dpi = 300)
```


# Statistical analyses of additional outcomes from the Eriksen Flanker Task 

## Mean reaction time in the incompatible and compatible flanker task condition

### Incompatible task condition

*Fit linear mixed-effects model, check model assumptions and extract performance metrics* 

```{r}
set.seed(123)

RT_incompatible_mod <- lmer(RT_incompatible ~ Light + IIV_TST + (1 | Subject),
                            data = Flanker_data
                            )
```

```{r}
performance::check_model(RT_incompatible_mod)

plot(DHARMa::simulateResiduals(RT_incompatible_mod))
```

```{r}
performance::model_performance(RT_incompatible_mod)
```

*Extract results and model-based parameters* 

```{r}
summary(RT_incompatible_mod)
```

```{r}
parameters::model_parameters(RT_incompatible_mod)
```

*Calculate approximated partial Cohen's f^2 as effect size for all fixed effects irrespective of significance, based on test statistics (output from summary() above)*

SWL:

```{r}
effectsize::t_to_f2(t = 0.885, df = 105.2612, ci = 0.95, partial = TRUE)
```

LWL:

```{r}
effectsize::t_to_f2(t = -0.092, df = 105.5736, ci = 0.95, partial = TRUE)
```

BWL:

```{r}
effectsize::t_to_f2(t = 0.302, df = 103.8599, ci = 0.95, partial = TRUE)
```

Intra-individual sleep variability:

```{r}
effectsize::t_to_f2(t = -0.480, df =  97.7794, ci = 0.95, partial = TRUE)
```


### Compatible task condition 

*Fit linear mixed-effects model, check model assumptions and extract performance metrics* 

```{r}
set.seed(123)

RT_compatible_mod <- lmer(RT_compatible ~ Light + IIV_TST + (1 | Subject),
                          data = Flanker_data
                          )
```

```{r}
performance::check_model(RT_compatible_mod)

plot(DHARMa::simulateResiduals(RT_compatible_mod))
```

```{r}
performance::model_performance(RT_compatible_mod)
```

*Extract results and modelbased parameters* 

```{r}
summary(RT_compatible_mod)
```

```{r}
parameters::model_parameters(RT_compatible_mod)
```

*Calculate approximated partial Cohen's f^2 as effect size for all fixed effects irrespective of significance, based on test statistics (output from summary() above)*

SWL:

```{r}
effectsize::t_to_f2(t = 1.082, df = 106.7473, ci = 0.95, partial = TRUE)
```

LWL:

```{r}
effectsize::t_to_f2(t = -0.669, df = 107.0391, ci = 0.95, partial = TRUE)
```

BWL:

```{r}
effectsize::t_to_f2(t = 0.019, df = 104.8825, ci = 0.95, partial = TRUE)
```

Intra-individual sleep variability:

```{r}
effectsize::t_to_f2(t = -0.504, df =  80.7442, ci = 0.95, partial = TRUE)
```


## Mean accuracy in the incompatible and compatible flanker task condition

*Add a small constant to accuracy values = 1 so that it can be modelled with beta regression*

```{r}
Flanker_data <- Flanker_data %>% 
  mutate(
    Accuracy_compatible = ifelse(Accuracy_compatible == 1, 1 - 0.00001, Accuracy_compatible),
    Accuracy_incompatible = ifelse(Accuracy_incompatible == 1, 1 - 0.00001, Accuracy_incompatible)
    )
```


### Incompatible task condition

*Fit generalized linear mixed-effects model assuming with a beta distribution and logit link function and extract performance metrics*

```{r}
set.seed(123)

Accuracy_incompatible_mod <- glmmTMB(Accuracy_incompatible ~ Light + IIV_TST + (1 | Subject),
                                    data = Flanker_data,
                                    family = beta_family(link = "logit")
                                    )
```

```{r}
performance::model_performance(Accuracy_incompatible_mod)
```

*Extract results and modelbased parameters* 

```{r}
summary(Accuracy_incompatible_mod)
```

```{r}
parameters::model_parameters(Accuracy_incompatible_mod)
```

*Calculate approximated partial r as effect size for all fixed effects irrespective of significance, based on test statistics (output from summary() above)*

SWL: 

```{r}
z_to_r(z = 0.616, n = 39, ci = 0.95, partial = TRUE)
```

LWL:

```{r}
z_to_r(z = -0.369, n = 39, ci = 0.95, partial = TRUE)
```

BWL:

```{r}
z_to_r(z = 0.367, n = 39, ci = 0.95, partial = TRUE)
```

Intra-individual sleep variability:

```{r}
z_to_r(z = -0.269, n = 39, ci = 0.95, partial = TRUE)
```


### Compatible task condition 

*Fit generalized linear mixed-effects model assuming with a beta distribution and logit link function and extract performance metrics*

```{r}
set.seed(123)

Accuracy_compatible_mod <- glmmTMB(Accuracy_compatible ~ Light + IIV_TST + (1 | Subject),
                                  data = Flanker_data,
                                  family = beta_family(link = "logit")
                                  )
```

```{r}
performance::model_performance(Accuracy_compatible_mod)
```

*Extract results and modelbased parameters* 

```{r}
summary(Accuracy_compatible_mod)
```

```{r}
parameters::model_parameters(Accuracy_compatible_mod)
```

*Calculate approximated partial r as effect size for all fixed effects irrespective of significance, based on test statistics (output from summary() above)*

SWL: 

```{r}
z_to_r(z = 0.378, n = 39, ci = 0.95, partial = TRUE)
```

LWL:

```{r}
z_to_r(z = -0.439, n = 39, ci = 0.95, partial = TRUE)
```

BWL:

```{r}
z_to_r(z = -0.171, n = 39, ci = 0.95, partial = TRUE)
```

Intra-individual sleep variability: 

```{r}
z_to_r(z = 0.881, n = 39, ci = 0.95, partial = TRUE)
```
